---
params: 
  title: ""
  publication_date: ""
  doi: ""
  github: ""
  lang: ""
output:
  html_document:
    anchor_sections: false
    theme: null
    highlight: null
    mathjax: null
    css: ["style.css", "https://fonts.googleapis.com/css?family=Source+Sans+Pro:400,700&display=swap"]
    self_contained: true
# To produce Word output, just comment the output lines above and uncomment
# the ones here.
# output: word_document
# always_allow_html: yes
title: "`r params$title`"
editor_options: 
  chunk_output_type: console
---

```{r general-setup, include=FALSE}
## This file contains the ENGLISH version of the data story

# Set general chunk options
knitr::opts_chunk$set(
  echo = FALSE, fig.showtext = TRUE, fig.retina = 3, out.width = "100%",
  fig.height = 4, fig.align = "center", warning = FALSE, message = FALSE
)

# Install snf.datastory package if not available, otherwise load it
if (!require("snf.datastory")) {
  if (!require("devtools")) {
    install.packages("devtools")
    library(devtools)
  }
  install_github("snsf-data/snf.datastory")
  library(snf.datastory)
}

# Load packages
library(tidyverse)
library(lubridate)
library(tidytext)
library(scales)
library(conflicted)
library(jsonlite)
library(janitor)
library(here)
library(glue)
library(ggiraph)
library(gfonts)
library(systemfonts)

# Conflict preferences
conflict_prefer("filter", "dplyr")
conflict_prefer("get_datastory_theme", "snf.datastory")
conflict_prefer("get_datastory_scheme", "snf.datastory")

# Increase showtext package font resolution
showtext_opts(dpi = 320)

# Set the locale for date formatting (Windows)
if (Sys.info()[["sysname"]] == "Windows") Sys.setlocale("LC_TIME", "English")

# Create function to print number with local language-specific format
print_num <- function (x,
                       lang = if_else(params$lang != "", params$lang, "en"))
{
  
  if (lang == "en") 
    prettyNum(x, big.mark = ",", decimal.mark = ".")
  else if (lang == "de") 
    prettyNum(x, big.mark = "", decimal.mark = ",")
  else if (lang == "fr") 
    prettyNum(x, big.mark = "", decimal.mark = ",")
  
}

# Need to register the font to allow its use by ggiraph when creating SVG files
if(!font_family_exists("Source Sans Pro")){
  
  # Check if the font already exist in the repository
  if (!file.exists(here("fonts", "css", "source-sans-pro.css"))) {
    
    # Required to make available the Source Sans Pro to ggiraph to create the
    # SVG for interactive plots.
    setup_font(
      id = "source-sans-pro", 
      output_dir = "fonts", 
      variants = c("regular", "italic", "700", "700italic"), 
      prefer_local_source = FALSE
    )
    
  }
  
  # Ensure rendering of Source Sans Pro is possible for the reader even if not
  # installed (required for ggiraph)
  use_font("source-sans-pro", "fonts/css/source-sans-pro.css",
           selector = ".dummy-selector")
  
  # Register existing/downloaded fonts
  register_font(
    name = "Source Sans Pro", 
    plain = list("fonts/fonts/source-sans-pro-v21-latin-regular.woff", 0), 
    bold = list("fonts/fonts/source-sans-pro-v21-latin-700.woff", 0), 
    italic = list("fonts/fonts/source-sans-pro-v21-latin-italic.woff", 0),
    bolditalic = list("fonts/fonts/source-sans-pro-v21-latin-700italic.woff", 0)
  )
}

# Knitr hook for local formatting of printed numbers
knitr::knit_hooks$set(
  inline = function(x) {
    if (!is.numeric(x)) {
      x
    } else {
      print_num(x)
    }
  }
)

# Produce an interactive figure with ggiraph based on a ggplot object
make_ggiraph <- function(x,                    # ggplot object
                         h = 4,                # height of the svg generated
                         sw = 2,               # width of the stroke
                         fcolor = "#f6685e",   # color (fill)
                         color = NA,           # color
                         scolor = "#f6685e") { # color of the stroke
  girafe(
    ggobj = x,
    height_svg = h,
    options = list(
      opts_toolbar(saveaspng = FALSE),
      opts_hover(
        css =
          glue("fill:{fcolor};color:{color};stroke:{scolor};stroke-width:{sw};")
      ),
      opts_tooltip(
        css = get_ggiraph_tooltip_css(),
        opacity = 0.8,
        delay_mouseover = 0,
        delay_mouseout = 0
      )
    )
  )
}

```

```{r print-header-infos, results='asis'}

# Add publication date to header
cat(format(as_datetime(params$publication_date), "%d.%m.%Y"))

```

```{r data-load, include=FALSE}

# Data to be used in the data story
dat <-
  read_csv2(here("data", "data.csv")) |>
  mutate(
    research_area =
      fct_recode(
        research_area,
        SSH = "Humanities and Social Sciences",
        MINT = "Mathematics, Natural and\nEngineering Sciences",
        LS = "Biology and Medicine"),
    research_area = fct_relevel(research_area, "LS", after = Inf)
  )

# Anonymized data on success rate to be used in the data story
success_dat <-
  read_csv2(here("data", "success_rate_anonymized_data.csv")) |>
  mutate(
    research_area =
      fct_recode(
        research_area,
        SSH = "Humanities and Social Sciences",
        MINT = "Mathematics, Natural and\nEngineering Sciences",
        LS = "Biology and Medicine"),
    research_area = fct_relevel(research_area, "LS", after = Inf)
  )

```

```{r in-text-data-1, include=FALSE}

# This chunk generates generic data used in-text as well as in the introduction

# Percentage of amount granted dedicated to project partners
partner_budget_all <-
  dat |>
  group_by(snf_grant_number) |>
  summarise(
    sum_partner = sum(partner_budget, na.rm = TRUE),
    amount_granted = unique(amount_granted)
  ) |>
  ungroup() |>
  summarise(
    pct_partner_budget = sum(sum_partner) / sum(amount_granted, na.rm = TRUE)
  )

# Percentage of amount granted dedicated to project partners outside Switzerland
partner_budget_outside_ch <-
  dat |>
  group_by(snf_grant_number) |>
  summarise(
    sum_partner =
      sum(
        partner_budget[role == "Projektpartner" & iso_code != "CH"],
        na.rm = TRUE
      ),
    amount_granted = unique(amount_granted)
  ) |>
  ungroup() |>
  summarise(
    pct_partner_budget = sum(sum_partner) / sum(amount_granted, na.rm = TRUE)
  )

# Percentage of funded grants with project partners
proj_fund_with_partners <-
  dat |>
  group_by(snf_grant_number) |> 
  summarise(n = sum(role == "Projektpartner", na.rm = TRUE) > 0) |>
  ungroup() |>
  pull(n) |>
  mean()

# Number of funded grants with project partners
n_proj_ch <-
  dat |>
  group_by(snf_grant_number) |>
  summarise(
    n =
      sum(role == "Projektpartner" & iso_code == "CH", na.rm = TRUE) > 0
  ) |>
  ungroup() |>
  pull(n) |>
  sum()

# Number of funded grants with project partners from Europe (excl. CH)
n_proj_europe <-
  dat |>
  group_by(snf_grant_number) |>
  summarise(
    n =
      sum(
        role == "Projektpartner" & iso_code != "CH" & continent == "Europe",
        na.rm = TRUE
      ) > 0
  ) |>
  ungroup() |>
  pull(n) |>
  sum()

# Number of funded grants with project partners from North America
n_proj_northam <-
  dat |>
  group_by(snf_grant_number) |>
  summarise(
    n =
      sum(
        role == "Projektpartner" & iso_code %in% c("US", "CA"),
        na.rm = TRUE
      ) > 0
  ) |>
  ungroup() |>
  pull(n) |>
  sum()

# Number of funded grants with project partners from outside Europe
n_proj_world <-
  dat |>
  group_by(snf_grant_number) |>
  summarise(
    n =
      sum(
        role == "Projektpartner" & continent != "Europe",
        na.rm = TRUE
      ) > 0
  ) |>
  ungroup() |>
  pull(n) |>
  sum()

# Summary data on average number of partners over years and research area
ave_part_in_projet_incl_part_years <-
  dat |>
  group_by(year, research_area, snf_grant_number) |>
  summarise(n_partners = sum(role == "Projektpartner", na.rm = TRUE)) |>
  filter(n_partners > 0) |>
  group_by(year, research_area) |>
  summarise(n_partners = mean(n_partners), n_proj = n()) |>
  ungroup() |>
  mutate(data_id = row_number())

```

**Since 2017, project partners can contribute to specific aspects of research projects supported by the SNSF's Project funding scheme. How often are project partners involved? Are there differences between research areas? In which countries are project partners based?**

<a href="https://www.snf.ch/en/WAvYcY7awAUGolST/funding/projects/projects-in-all-disciplines" target="_blank">Project funding</a> is the largest funding scheme of the SNSF; every year, it approves around 500 million francs for selected projects. As of grants funded in 2017, applicants have been able to include partners in their applications. Project partners are expected to make a partial contribution without being responsible for the project, and their contribution can be financed from the project budget.

Since applicants have been able to involve project partners, the SNSF approved a total of `r print_num(length(unique(dat$snf_grant_number)))` applications for Project funding, not including the internationally focused <a href="https://www.snf.ch/en/j3eRKmgqIrepqJnT/funding/projects/weave-lead-agency" target="_blank">Weave/Lead Agency</a> proposals. Among these funded projects, `r round(proj_fund_with_partners * 100)`% involved collaboration with one or more project partners. The average number of project partners per grant increased from 2017 to 2018 (from `r round(ave_part_in_projet_incl_part_years |> filter(year == "2017") |> summarise(mean = weighted.mean(n_partners, n_proj)) |> pull(mean), 1)` to `r round(ave_part_in_projet_incl_part_years |> filter(year == "2018") |> summarise(mean = weighted.mean(n_partners, n_proj)) |> pull(mean), 1)`), but their number has remained stable since then.

<div class='info-box'>

<p><b>Collaboration with researchers in Switzerland and abroad</b></p>

Unlike Project funding applicants, project partners may be affiliated with a foreign institution. One of the benefits of project partners is to promote Swiss research and facilitate collaboration with both the national and international research community. This is illustrated by the fact that since 2017,  `r round((n_proj_ch / length(unique(dat$snf_grant_number))) * 100)`% of approved Project funding grants reported at least one partnership with a researcher at a Swiss institution, `r round((n_proj_europe / length(unique(dat$snf_grant_number))) * 100)`% included at least one partner from a research institution in Europe (excluding Switzerland), and `r round(n_proj_world / length(unique(dat$snf_grant_number)) * 100)`% partnered with at least one researcher from an institution outside Europe.

Up to 20% of an individual project’s budget may be allocated to project partners to contribute directly to the project. In practice, about `r round(partner_budget_all$pct_partner_budget * 100)`% of the overall Project funding budget is directed to project partners, with `r round(partner_budget_outside_ch$pct_partner_budget * 100)`% to researchers outside of Switzerland.

</div>

### Differences between research areas

```{r in-text-data-2, include=FALSE}

# This chunk generate data used in-text regarding number of project partners
# over years and across research areas.

# Percentage of projects including partners over years and research area
pct_proj_with_part_years <-
  dat |>
  group_by(year, research_area, snf_grant_number) |>
  summarise(n_partners = sum(role == "Projektpartner", na.rm = TRUE) > 0) |>
  group_by(year, research_area) |>
  summarise(n_partners = mean(n_partners), n_proj = n()) |>
  ungroup() |>
  mutate(data_id = row_number())

# Percentage of projects including partners over years
ave_pct_proj_with_part_years <-
  dat |>
  group_by(year, snf_grant_number) |>
  summarise(n = sum(role == "Projektpartner", na.rm = TRUE) > 0) |>
  group_by(year) |>
  summarise(n_partners = mean(n))

```


Across the three research areas, social sciences and humanities (SSH), mathematics, natural and engineering sciences (MINT), and life sciences (LS), the percentage of funded grants with at least one project partner has increased slightly since the introduction of projects partners, from `r round(filter(ave_pct_proj_with_part_years, year == 2017)$n_partners * 100)`% in 2017 to `r round(filter(ave_pct_proj_with_part_years, year == 2022)$n_partners * 100)`% in 2022. Comparing the different research areas, the percentage of funded grants that included project partners, as well as the average number of project partners, has been lower in MINT.

```{r data-fig-1-and-2, include=FALSE}

# Figure 1 (ggplot)
pct_proj_with_part_years_fig <-
  pct_proj_with_part_years |>
  ggplot() +
  aes(
    x = year,
    y = n_partners,
    color = research_area,
    tooltip =
      glue(
        "Year: {year}<br>",
        "Research area: {research_area}<br>",
        "<b>Percentage of funded grants with<br>",
        "project partners: {round(n_partners * 100)}%</b>"
      ),
    data_id = data_id
  ) +
  geom_line(aes(tooltip = NULL)) +
  geom_point_interactive(size = 2.5, stroke = 0.2) +
  geom_text(
    data =
      filter(
        pct_proj_with_part_years,
        year == 2021
      ),
    aes(
      label = research_area,
      y = n_partners + 0.035,
      x = year
    ),
    size = 3,
    hjust = 0.5,
    family = "Source Sans Pro",
    fontface = "bold"
  ) +
  coord_cartesian(ylim = c(0, 1)) +
  scale_y_continuous(labels = percent) +
  scale_color_manual(values = get_datastory_scheme(n_col = 3)) +
  get_datastory_theme(gridline_axis = "y", legend_position = "")

# Figure 2 (ggplot)
ave_part_in_projet_incl_part_years_fig <-
  ave_part_in_projet_incl_part_years |>
  ggplot() +
  aes(
    x = year,
    y = n_partners, 
    color = research_area,
    tooltip =
      glue(
        "Year: {year}<br>",
        "Research area: {research_area}<br>",
        "<b>Number of project partners: {round(n_partners, 2)}</b>"
      ),
    data_id = data_id) +
  geom_line(aes(tooltip = NULL)) +
  geom_point_interactive(size = 2.5, stroke = 0.2) +
  geom_text(
    data =
      filter(
        ave_part_in_projet_incl_part_years,
        year == 2022
      ),
    aes(
      label = research_area,
      y = n_partners,
      x = year + 0.1
    ),
    size = 3,
    hjust = 0,
    family = "Source Sans Pro",
    fontface = "bold"
  ) +
  coord_cartesian(ylim = c(0, 4), xlim = c(2017, 2022.25)) +
  scale_color_manual(values = get_datastory_scheme(n_col = 3)) +
  get_datastory_theme(gridline_axis = "y", legend_position = "")

```

<div class="hide-mobile hide-tablet widemedia">
<div class="plot-box">
<div class="plot-title">Percentage of funded grants with project partners</div>
```{r fig-1-desk}

# This figure is only visible on desktop devices
make_ggiraph(pct_proj_with_part_years_fig)

```
<br>
<div class="plot-title">Average number of project partners in grants that included project partners</div>

```{r fig-2-desk}

# This figure is only visible on desktop devices
make_ggiraph(ave_part_in_projet_incl_part_years_fig)

```

</div>
</div>

<div class="hide-desktop">
<div class="plot-box">
<div class="plot-title">Percentage of funded grants with project partners</div>
```{r fig-1-phone}

# This figure is only visible on phone and tablet devices
make_ggiraph(pct_proj_with_part_years_fig)

```
<br>
<div class="plot-title">Average number of project partners in grants that included project partners</div>

```{r fig-2-phone}

# This figure is only visible on phone and tablet devices
make_ggiraph(ave_part_in_projet_incl_part_years_fig)

```
</div>
</div>

```{r institutions-data, include=FALSE}

institutions_order <-
  c(
    "Cantonal universities",
    "ETH domain",
    "Universities of applied sciences",
    "Universities of teacher education",
    "Other research institutions"
  )

# Summary data about project partners over years and as a function of
# institution type.
proj_partners_inst_years <-
  dat |>
  group_by(snf_grant_number, year) |>
  mutate(n_partners = sum(role == "Projektpartner", na.rm = TRUE)) |>
  filter(role != "Projektpartner") |>
  summarise(
    n_partners = unique(n_partners),
    is_eth =
      sum(
        research_institution_type == "ETH domain",
        na.rm = TRUE
      ) > 0,
    is_cant =
      sum(
        research_institution_type == "Cantonal University",
        na.rm = TRUE
      ) > 0,
    is_applied =
      sum(
        research_institution_type == "University of Applied Sciences",
        na.rm = TRUE
      ) > 0,
    is_other =
      sum(
        research_institution_type == "Other research institutions",
        na.rm = TRUE
      ) > 0,
    is_edu =
      sum(
        research_institution_type == "University of Teacher Education",
        na.rm = TRUE
      ) > 0,
  ) |>
  ungroup() |>
  pivot_longer(
    cols = starts_with("is_"), names_to = "institution", values_to = "value"
  ) |>
  filter(value) |>
  mutate(
    institution =
      fct_recode(
        institution,
        `Cantonal universities` = "is_cant",
        `ETH domain` = "is_eth",
        `Universities of applied sciences` = "is_applied",
        `Universities of teacher education` = "is_edu",
        `Other research institutions` = "is_other"
      ),
    institution = fct_relevel(institution, institutions_order)
  ) |>
  group_by(institution, year) |>
  summarise(
    n_proj_with_partner = sum(n_partners > 0) / n(),
    ave_n_partner = mean(n_partners),
    n_proj = n()
  ) |>
  ungroup() |>
  mutate(data_id = row_number())

```

### Universities of applied sciences have the highest proportion of project partners

The Swiss research landscape is composed of different types of institutions, with different roles and scientific purposes. Funded grants with at least one applicant from a university of applied sciences included the highest percentage of project partners (`r round(proj_partners_inst_years |> filter(str_detect(institution, "applied")) |> summarise(mean = weighted.mean(n_proj_with_partner, n_proj)) |> pull(mean) * 100)`%) over the six years analysed. Grants with an applicant from a university of teacher education (`r round(proj_partners_inst_years |> filter(str_detect(institution, "teacher")) |> summarise(mean = weighted.mean(n_proj_with_partner, n_proj)) |> pull(mean) * 100)`%) or an "other" type of research institution  (`r round(proj_partners_inst_years |> filter(str_detect(institution, "Other")) |> summarise(mean = weighted.mean(n_proj_with_partner, n_proj)) |> pull(mean) * 100)`%) included more project partners than cantonal universities (`r round(proj_partners_inst_years |> filter(str_detect(institution, "Cantonal")) |> summarise(mean = weighted.mean(n_proj_with_partner, n_proj)) |> pull(mean) * 100)`%), and the lowest percentage came from the ETH domain (`r round(proj_partners_inst_years |> filter(str_detect(institution, "ETH")) |> summarise(mean = weighted.mean(n_proj_with_partner, n_proj)) |> pull(mean) * 100)`%). This is consistent with the previous figures, where we observed that MINT proposals tend to include fewer project partners, and ETH domain institutions have a much higher percentage of MINT proposals compared to the other categories.

```{r data-fig-3, include=FALSE}

# Figure 3 (ggplot)
proj_partners_inst_years_fig <-
  proj_partners_inst_years |>
  ggplot() +
  aes(
    x = year,
    y = n_proj_with_partner,
    color = institution,
    tooltip =
      glue(
        "Year: {year}<br>",
        "Research institution: {institution}<br>",
        "<b>Percentage of funded grants with<br>",
        "project partners: {round(n_proj_with_partner * 100, 1)}%</b>"
      ),
    data_id = data_id) +
  geom_line(aes(tooltip = NULL)) +
  geom_point_interactive(size = 2.5, stroke = 0.2) +
  geom_text(
    data =
      filter(
        proj_partners_inst_years,
        (
          year == 2021 & institution %in% c("Cantonal universities",
                                            "ETH domain",
                                            "Universities of teacher education")
        ) |
          (
            year == 2022 & institution %in% c("Other research institutions",
                                              "Universities of applied sciences")
          )
      ),
    aes(
      label = str_wrap(institution, 20),
      y =
        case_when(
          institution == "Universities of teacher education"
          ~ n_proj_with_partner + 0.1,
          
          institution %in% c("ETH domain", "Cantonal universities")
          ~ n_proj_with_partner - 0.025,
          
          institution == "Other research institutions"
          ~ n_proj_with_partner + 0.0625,
          
          TRUE ~ n_proj_with_partner + 0.0125
        ),
      x =
        if_else(
          year == 2022, year + 0.125, year
        ),
      hjust = if_else(year == 2022, 0, 0.5)
    ),
    vjust = 1,
    size = 3,
    family = "Source Sans Pro",
    fontface = "bold"
  ) +
  scale_color_manual(values = get_datastory_scheme()[-4]) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = c(2017:2022)) +
  coord_cartesian(xlim = c(2017, 2023.25), ylim = c(0, 1)) +
  get_datastory_theme(gridline_axis = "y", legend_position = "")

```

<div class="hide-mobile hide-tablet widemedia">
<div class="plot-box">
<div class="plot-title">Percentage of funded grants with project partners by research institution type</div>
```{r fig-3-desk}

# This figure is only visible on desktop devices
make_ggiraph(proj_partners_inst_years_fig)

```
</div>
</div>

<div class="hide-desktop">
<div class="plot-box">
<div class="plot-title">Percentage of funded grants with project partners by research institution type</div>
```{r fig-3-phone}

# This figure is only visible on phone and tablet devices
make_ggiraph(proj_partners_inst_years_fig)

```
</div>
</div>

### Where are project partners based?

```{r world-region, include=FALSE}

# This chunk generate summary data about percentage over years of funded grants
# involving partners from different region of the world.

world_region_area_years_app <-
  dat |>
  select(
    snf_grant_number, world_region, research_area, year, role, iso_code
  ) |>
  group_by(research_area, year, snf_grant_number) |>
  summarise(
    Switzerland =
      sum(
        role == "Projektpartner" & iso_code == "CH",
        na.rm = TRUE
      ) > 0,
    `Europe (excl.\nSwitzerland)` =
      sum(
        role == "Projektpartner" & world_region == "Europe" & iso_code != "CH",
        na.rm = TRUE
      ) > 0,
    Oceania =
      sum(
        role == "Projektpartner" & world_region == "Oceania",
        na.rm = TRUE
      ) > 0,
    Asia =
      sum(
        role == "Projektpartner" & world_region == "Asia",
        na.rm = TRUE
      ) > 0,
    `Latin America` =
      sum(
        role == "Projektpartner" & world_region == "Latin America",
        na.rm = TRUE
      ) > 0,
    `North America` =
      sum(
        role == "Projektpartner" & world_region == "North America",
        na.rm = TRUE
      ) > 0,
    Africa = 
      sum(
        role == "Projektpartner" & world_region == "Africa",
        na.rm = TRUE
      ) > 0,
    `No project\npartner` =
      mean(role != "Projektpartner", na.rm = TRUE) == 1
  ) |>
  ungroup() |>
  pivot_longer(
    Switzerland:`No project\npartner`,
    values_to = "region_involved",
    names_to = "world_region"
  ) |>
  group_by(research_area, year, world_region) |>
  summarise(
    mean = mean(region_involved),
    n = sum(region_involved)
  ) |>
  ungroup() |>
  mutate(
    world_region = fct_reorder(world_region, mean, sum, .desc = TRUE),
    without_partner = world_region == "No project\npartner"
  )

```

```{r in-text-data-3, include=FALSE}

# This chunk generate data used in-text about international aspect of project
# partners.

other_regions_pct_proj <-
  dat |>
  group_by(snf_grant_number) |>
  summarise(
    part =
      sum(
        role == "Projektpartner" & world_region %in% c("Asia", "Oceania",
                                                       "Africa",
                                                       "Latin America"),
        na.rm = TRUE
      ) > 0
  ) |>
  ungroup() |>
  summarise(pct = mean(part, na.rm = TRUE))

abroad_part_discipline <-
  dat |>
  group_by(snf_grant_number, research_area) |>
  summarise(
    mean =
      sum(role == "Projektpartner", na.rm = TRUE) > 0
    &
      sum(iso_code[role == "Projektpartner"] != "CH", na.rm = TRUE) > 0
  ) |>
  group_by(research_area) |>
  summarise(mean = mean(mean))

```

In contrast to applicants, who must be affiliated with a Swiss research institution to submit a proposal, there are no restrictions on the geographical location of project partners. In practice, most project partners are based in Switzerland or the rest of Europe, with `r round(n_proj_ch / length(unique(dat$snf_grant_number)) * 100)`% of funded grants having at least one project partner from Switzerland, `r round(n_proj_europe / length(unique(dat$snf_grant_number)) * 100)`% with at least one from Europe (excluding Switzerland), and `r round(n_proj_northam / length(unique(dat$snf_grant_number)) * 100)`% with at least one from North America (USA and Canada). Regarding the other regions of the world, only `r round(other_regions_pct_proj * 100)`% of funded grants included at least one project partner from Asia, Oceania, Africa or Latin America (South America and Mexico).

```{r data-fig-4, include=FALSE}

# Factors with the different world regions used in the figure
world_region_levels <-
  fct_relevel(
    world_region_area_years_app$world_region,
    "No project\npartner", after = Inf
  ) |>
  levels()

# Colors for the different world regions used in the figure
world_region_colors <-
  get_datastory_scheme(
    n_col = length(world_region_levels)
  )[-4]
world_region_colors[str_starts(world_region_levels, "No p")] <- "#808080"
  
# Figure 4 (ggplot)
world_region_area_years_app_fig <-
  world_region_area_years_app |>
  mutate(
    data_id = 1:n(),
    world_region = fct_relevel(world_region, world_region_levels)
  ) |>
  ggplot() +
  aes(
    x = year,
    y = mean,
    color = world_region,
    linetype = world_region,
    tooltip =
      if_else(
        world_region != "No project\npartner",
        glue(
          "Year: {year}<br>",
          "Research area: {research_area}<br>",
          "<b>Percentage of funded grants with at least<br>",
          "one partner from {world_region}: {round(mean * 100, 1)}%</b>"
        ),
        glue(
          "Year: {year}<br>",
          "Research area: {research_area}<br>",
          "<b>Percentage of funded grants without<br>",
          "project partner: {round(mean * 100, 1)}%</b>"
        )
      ),
    data_id = data_id
  ) +
  geom_line(aes(tooltip = NULL)) +
  geom_point_interactive(size = 2.5, stroke = 0.2) +
  coord_cartesian(ylim = c(0, 0.8)) +
  scale_color_manual(values = world_region_colors) +
  scale_linetype_manual(
    labels = world_region_levels,
    values = c(1, 1, 1, 1, 1, 1, 1, 8)
  ) +
  scale_y_continuous(labels = scales::percent) +
  facet_wrap(~research_area, ncol = 2) +
  get_datastory_theme(gridline_axis = "y") +
  theme(
    legend.position = c(0.575, 0.05),
    legend.justification = c(0, 0),
    legend.key.width = unit(2, "lines")
  ) +
  guides(
    colour = guide_legend(ncol = 2),
    linetype = guide_legend(ncol = 2)
  )

```

<div class="hide-mobile hide-tablet widemedia">
<div class="plot-box">
<div class="plot-title">Share of funded grants with project partners, by project partner region</div>
```{r fig-4-desk}

# This figure is only visible on desktop devices
make_ggiraph(world_region_area_years_app_fig)

```
</div>
</div>

<div class="hide-desktop">
<div class="plot-box">
<div class="plot-title">Share of funded grants with project partners, by project partner region</div>
```{r fig-4-phone}

# This figure is only visible on tablet and phone devices
make_ggiraph(world_region_area_years_app_fig)

```
</div>
</div>

In SSH, the percentage of funded grants that included a project partner from Europe (`r round(filter(world_region_area_years_app, research_area == "SSH") |> group_by(world_region) |> summarise(mean = weighted.mean(mean, n)) |> filter(world_region == "Europe (excl.\nSwitzerland)") |> pull(mean) * 100)`%) or from North America (`r round(filter(world_region_area_years_app, research_area == "SSH") |> group_by(world_region) |> summarise(mean = weighted.mean(mean, n)) |> filter(world_region == "North America") |> pull(mean) * 100)`%) is higher compared to the other research areas. In LS, only `r round(filter(world_region_area_years_app, research_area == "LS") |> group_by(world_region) |> summarise(mean = weighted.mean(mean, n)) |> filter(world_region == "Europe (excl.\nSwitzerland)") |> pull(mean) * 100)`% of funded grants included a project partner from Europe and `r round(filter(world_region_area_years_app, research_area == "LS") |> group_by(world_region) |> summarise(mean = weighted.mean(mean, n)) |> filter(world_region == "North America") |> pull(mean) * 100)`% from North America, and in MINT it was `r round(filter(world_region_area_years_app, research_area == "MINT") |> group_by(world_region) |> summarise(mean = weighted.mean(mean, n)) |> filter(world_region == "Europe (excl.\nSwitzerland)") |> pull(mean) * 100)`% and `r round(filter(world_region_area_years_app, research_area == "MINT") |> group_by(world_region) |> summarise(mean = weighted.mean(mean, n)) |> filter(world_region == "North America") |> pull(mean) * 100)`%. While grants funded in SSH included relatively more project partners from abroad (`r round(abroad_part_discipline$mean[abroad_part_discipline$research_area == "SSH"] * 100)`%) compared to MINT (`r round(abroad_part_discipline$mean[abroad_part_discipline$research_area == "MINT"] * 100)`%) and LS (`r round(abroad_part_discipline$mean[abroad_part_discipline$research_area == "LS"] * 100)`%), MINT had the highest percentage of project partners from Asia (`r round(world_region_area_years_app |> filter(research_area == "MINT", world_region == "Asia") |> summarise(mean = weighted.mean(mean, n)) |> pull(mean) * 100)`%).

```{r country-partner, include=FALSE}

# This chunk generate summary data on the percentage of project including
# partners from different countries (only most represented are used).
partners_country_area <-
  dat |>
  drop_na(country) |>
  filter(iso_code != "CH") |>
  count(country, research_area, world_region) |>
  group_by(research_area) |>
  mutate(pct = n / sum(n)) |>
  ungroup() |>
  mutate(
    country = fct_reorder(country, n, sum),
    world_region = fct_reorder(world_region, n, sum, .desc = TRUE)
  ) |>
  arrange(desc(n)) |>
  filter(
    country %in% levels(country)[
      (length(levels(country))-14):length(levels(country))
    ]) |>
  mutate(data_id = 1:n()) |>
  ungroup()

```


The following figure shows the 15 most represented countries per research area (excluding Switzerland). Across all research areas, project partners are mostly located in the `r partners_country_area |> group_by(country) |> summarise(pct = weighted.mean(pct, n)) |> arrange(desc(pct)) |> slice(1) |> pull(country) |> as.character()` (`r round(partners_country_area |> group_by(country) |> summarise(pct = weighted.mean(pct, n)) |> arrange(desc(pct)) |> slice(1) |> pull(pct) * 100)`%) followed by `r partners_country_area |> group_by(country) |> summarise(pct = weighted.mean(pct, n)) |> arrange(desc(pct)) |> slice(2) |> pull(country) |> as.character()` (`r round(partners_country_area |> group_by(country) |> summarise(pct = weighted.mean(pct, n)) |> arrange(desc(pct)) |> slice(2) |> pull(pct) * 100)`%) and `r partners_country_area |> group_by(country) |> summarise(pct = weighted.mean(pct, n)) |> arrange(desc(pct)) |> slice(3) |> pull(country) |> as.character()` (`r round(partners_country_area |> group_by(country) |> summarise(pct = weighted.mean(pct, n)) |> arrange(desc(pct)) |> slice(3) |> pull(pct) * 100)`%). The figure confirms the reported observation that project partners are mostly located in Europe (`r partners_country_area |> group_by(research_area) |> summarise(n = sum(world_region == "Europe")) |> ungroup() |> summarise(n = mean(n)) |> pull(n)` countries in the 15 most represented in each area are from Europe), while other countries such as Canada, Australia and Japan are also in the top 15.

```{r data-fig-5}

# This figure use a trick from the 'tidytext' package to allow the different
# facets to have a different factor order on the x axis. See here for a code
# example: https://community.rstudio.com/t/facet-specific-ordering-for-stacked-bar-chart/40491/3)

# Figure 5 (ggplot)
partners_country_area_fig <-
  partners_country_area |>
  ggplot() +
  aes(
    x = pct,
    y = tidytext::reorder_within(country, pct, research_area),
    fill = world_region,
    tooltip =
      glue(
        "Research area: {research_area}<br>",
        "World region: {world_region}<br>",
        "<b>{round(pct * 100, 1)}% of project partners based in {
          if_else(
            country %in% c('United States of America',
                           'United Kingdom',
                           'Netherlands'),
            paste0('the ', country),
            as.character(country)
          )
        }<b>"
      ),
    data_id = data_id) +
  geom_col_interactive(color = "white") +
  geom_text_interactive(
    aes(label = paste(round(pct * 100, 1), "%"),
        x = pct),
    color = "black",
    family = "Source Sans Pro",
    size = 2.5,
    hjust = -0.15,
    show.legend = FALSE) +
  coord_cartesian(expand = FALSE) +
  facet_wrap(~research_area, ncol = 1, scales = "free_y") +
  scale_fill_manual(values = get_datastory_scheme()[-4]) +
  tidytext::scale_y_reordered() +
  scale_x_continuous(labels = scales::percent, limits = c(0, 0.23)) +
  get_datastory_theme(gridline_axis = "x", legend_position = "top")

```

<div class="hide-mobile hide-tablet widemedia">
<div class="plot-box">
<div class="plot-title">Top 15 most represented countries among project partners, by research area</div>
```{r fig-5-desk, fig.height=10}

# This figure is only visible on desktop devices
make_ggiraph(partners_country_area_fig, h = 10, sw = NA, scolor = "#FFFFFF")

```
</div>
</div>

<div class="hide-desktop">
<div class="plot-box">
<div class="plot-title">Top 15 most represented countries among project partners, by research area</div>
```{r fig-5-phone, fig.height=10}

# This figure is only visible on tablet and phone devices
make_ggiraph(partners_country_area_fig, h = 10, sw = NA, scolor = "#FFFFFF")

```
</div>
</div>

While the three most represented countries -- the USA, Germany and France -- are the same across research areas, we see that their rank varies. In SSH, Germany is the most represented, while in MINT and LS, the most common country for project partners is the USA. Looking at non-European countries, we see that grants funded in MINT have a substantially higher percentage of project partnerships with Japan, echoing the observation that MINT has relatively more project partners from Asia compared to the other research areas.

### Success rates of proposals with project partners

```{r partners-success, include=FALSE}

# This chunk generate data used in-text and for a figure on success rate and
# number of project partners in applications.

success_rate_size_area <-
  success_dat |>
  group_by(grant_id, is_approved, research_area) |>
  summarise(
    n_partners =
      case_when(
        n_partners > 3 ~ "3+",
        n_partners > 1 ~ "2-3",
        n_partners == 1 ~ "1",
        n_partners == 0 ~ "0"
      )
  ) |>
  group_by(n_partners, research_area) |>
  summarise(
    success_rate = mean(is_approved),
    n_proj = n()
  ) |>
  ungroup() |>
  mutate(
    n_partners = factor(n_partners)
  ) |>
  mutate(data_id = row_number())

success_partnership_status_ls <-
  success_rate_size_area |>
  filter(!is.na(n_proj), research_area == "LS") |>
  mutate(has_partner = n_partners != "0") |>
  group_by(has_partner) |>
  summarise(sr = weighted.mean(success_rate, n_proj))

```

The last figure shows the number of project partners included in Project funding proposals along with success rate (i.e. the percentage of proposals approved for funding). At the descriptive level, we see that the differences are small, with the exception of LS, where proposals with the highest success rates did not include project partners (`r round(success_partnership_status_ls$sr[!success_partnership_status_ls$has_partner] * 100)`%), compared to proposals including at least one project partner (`r round(success_partnership_status_ls$sr[success_partnership_status_ls$has_partner] * 100)`%).

```{r data-fig-6, include=FALSE}

# Figure 6 (ggplot)
success_rate_size_area_fig <-
  success_rate_size_area |>
  ggplot() +
  aes(
    x = research_area, y = success_rate,
    fill = n_partners, group = n_partners,
    tooltip =
      glue(
        "Number of project partner(s): {n_partners}<br>",
        "Research area: {research_area}<br>",
        "<b>Success rate: {round(success_rate * 100, 1)}%</b>"
      ),
    data_id = data_id
  ) +
  geom_col_interactive(position = position_dodge(), color = "white") +
  annotate(
    geom = "text",
    x =
      c(
        c(0.625, 0.875, 1.125, 1.375),
        c(0.625, 0.875, 1.125, 1.375) + 1,
        c(0.625, 0.875, 1.125, 1.375) + 2
      ),
    y = -0.05,
    label = rep(c("0", "1", "2-3", "3+"), 3),
    size = 3,
    color = "#4F4F4F",
    family = "Source Sans Pro"
  ) +
  annotate(
    geom = "text",
    x = c(1:3),
    y = 0.7,
    label = c("SSH", "MINT", "LS"),
    fontface = "bold",
    size = 3.5,
    family = "Source Sans Pro"
  ) +
  coord_cartesian(ylim = c(-.025, 0.8)) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = get_datastory_scheme(n_col = 5)[-4]) +
  labs(x = "Number of project partners") +
  get_datastory_theme(
    title_axis ="x",
    text_axis = "y",
    gridline_axis = "y",
    legend_position = ""
  )

```

<div class="hide-mobile hide-tablet widemedia">
<div class="plot-box">
<div class="plot-title">Success rate and number of project partners</div>
```{r fig-6-desk}

# This figure is only visible on desktop devices
make_ggiraph(success_rate_size_area_fig, sw = NA, scolor = "#FFFFFF")

```
</div>
</div>

<div class="hide-desktop">
<div class="plot-box">
<div class="plot-title">Success rate and number of project partners</div>
```{r fig-6-phone}

# This figure is only visible on tablet and phone devices
make_ggiraph(success_rate_size_area_fig, sw = NA, scolor = "#FFFFFF")

```
</div>
</div>

Research is a collaborative effort, and project partners represent one of the many ways that collaboration is supported in research projects. The SNSF will continue to monitor the use of project partners.

Data, text and code of this data story are <a href="`r params$github`" target="_blank">available on Github</a> and <a href="`r params$doi`" target="_blank">archived on Zenodo</a>.<br>DOI: `r str_remove(params$doi, "https://doi.org/")`

```{r prevent-internal-snsf-packages, include=FALSE}
# Internal SNSF packages must not be used in data stories, as their
# pre-processing functions are internal and the corporate design differs from
# the data portal.
if (any(c("snfverse", "snf.preprocessing", "snf.plot") %in%
        loadedNamespaces())) {
  stop(glue(
    "You must not use internal SNSF packages in data stories.",
    " Please resort to snf.datastory."
  ))
}
```
